---
title: "BA Assignment 1 Car Dataset"
author: "Kehinde Balogun"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

library(readr)

```

Loading Car data set

```{r}
Vehicle <- read.csv("Vehicle Dataset/car data.csv")

```
Calculating the mean of the Selling Price 

```{r}
SellingPrice_Avg <- mean(Vehicle$Selling_Price, na.rm = T)

SellingPrice_Avg
```

Calculating the median of the Selling Price 

```{r}
SellingPrice_Mod <- median(Vehicle$Selling_Price, na.rm = T)

SellingPriceMode <- SellingPrice_Mod [[1]]

```
Calculating the mode of the Km Driven

```{r}
KmDriven_Mod <- mlv(Vehicle$Kms_Driven, method = "mfv")

KmDriven_Mod

```
Arranging the vehicle dataset by the Car year

```{r}
library(dplyr)

Vehicle <- Vehicle %>%
  
  arrange(Year)
```
Calculaing the range between the Present Price and Selling Price as well as the Variance and Standard deviation of the Km Driven.

```{r}
vehicle_stat <- sapply(Vehicle, function(col) {
  range_Pp_Sp <- max(Vehicle$Present_Price, na.rm = TRUE) - min(Vehicle$Selling_Price, na.rm = TRUE)
  var_KmDriven <- var(Vehicle$Kms_Driven, na.rm = TRUE)
  std_KmDriven <- sd(Vehicle$Kms_Driven, na.rm = TRUE)
  
  list(
    Range = range_Pp_Sp,
    Variance = var_KmDriven,
    StandardDeviation = std_KmDriven
  )
})

```

Drawing Histogram for the Km Driven

```{r}
hist(Vehicle$Kms_Driven,
  breaks = 10, #Number of breaks in the histogram
  main = "Cars Distance Covered (In Km)",
  xlab = "Km Driven",
  ylab = "Frequency",
  col = "lightblue"
  
)
```

Drawing Histogram for the Selling Price of cars

```{r}
hist(Vehicle$Selling_Price,
  breaks = 10, #Number of breaks in the histogram
  main = "Selling Price of Cars",
  xlab = "Selling Price",
  ylab = "Frequency",
  col = "orange"
  
)
```
Drawing Histogram for the Present Price of cars

```{r}
hist(Vehicle$Present_Price,
  breaks = 10, #Number of breaks in the histogram
  main = "Present Price of Cars",
  xlab = "Present Price",
  ylab = "Frequency",
  col = "maroon"
  
)
```
Creating a boxplot of Present price by Km Driven

```{r}
library(ggplot2)

ggplot(Vehicle, aes(y = Present_Price, x = Kms_Driven, fill = Present_Price)) + 
  geom_boxplot() +
  labs(title = "Boxplot of Present Price by Km Driven",
       y = "Present Price", x = "Km Driven", fill = "Present Price") +
  theme_minimal()


```

